formula1

### 2019-12-25 inst/cook.Rmd
more work on new maxp()

```{r}
o <- function(Ul,Cl,startp,give=FALSE){
    small <- 1e-5  #  ensure start at an interior point
    if(missing(startp)){startp <- small*(1:4)+rep(0.1,4)}
    out <- maxp(H, startp=small*(1:4)+rep(0.1,4), give=TRUE, fcm=Ul,fcv=Cl)
		if(give){
			return(out)
		} else {
			return(out$value)
		}
}

>>>>

```{r}
o <- function(Ul,Cl,startp,give=FALSE){
    small <- 1e-4  #  ensure start at an interior point
    if(missing(startp)){startp <- small*(1:4)+rep(0.1,4)}
    out <- maxp(H, startp=small*(1:4)+rep(0.1,4), give=TRUE, fcm=Ul,fcv=Cl)
		if(give){
			return(out)
		} else {
			return(out$value)
		}
}

### 2019-12-25 inst/eurovision.Rmd
more work on new maxp()

```{r,checknull}
print(loglik(indep(maxp(euro2009)),euro2009))
print(loglik(indep(equalp(euro2009)),euro2009))
```

@@

```{r,orderplot}
m <- maxp(euro2009)  # likelihoods
points_scored <- rowSums(wiki_matrix,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,18),ylim=c(0,18),pch=16,
xlab="official order",ylab="my order",main="Eurovision 2009")
par(xpd=TRUE) # allow country names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[i],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

```{r}
plot(log(rowSums(wiki_matrix,na.rm=TRUE)),log(maxp(euro2009)),
     pch=16,xlab="points scored",ylab="MLE strength")
```

>>>>

```{r,checknull}
m <- maxp(euro2009)  # MLE
print(loglik(indep(m),euro2009))
print(loglik(indep(equalp(euro2009)),euro2009))
```

@@

```{r,orderplot}
points_scored <- rowSums(wiki_matrix,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-m)   # m = MLE
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,18),ylim=c(0,18),pch=16,
xlab="official order",ylab="my order",main="Eurovision 2009")
par(xpd=TRUE) # allow country names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[ox[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

```{r}
plot(log(rowSums(wiki_matrix,na.rm=TRUE)),log(m),
     pch=16,xlab="points scored",ylab="MLE strength")
```

### 2019-12-25 inst/formula1.Rmd
more work on new maxp()

m <- maxp(L2017)
ox <- rank(-points)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE) # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[oy[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

In the graph above, we see a certain amount of disagreement.  For
example, using F1 points scored places Hamilton first and Vettel
second; while `hyper2` places Vettel first and Hamilton second.  But
overall there seems to be some degree of correlation between the two,
and differences in detail.

>>>>

m <- maxp(L2017)
ox <- rank(-points) # negative because number 1 = largest number of points
oy <- rank(-m)      # negative because number 1 = largest strength
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

In the graph above, we see a certain amount of disagreement.  For
example, using F1 points scored places Hamilton first (363), Vettel
second (317), and Bottas third (305); while `hyper2` places Hamilton
first (0.29), Bottas second (0.17), and Vettel third (0.14).  Note
also the large number of players with zero points (who rank equal 23rd
by the F1 points system) but are nevertheless separated by
Bradley-Terry.  These players appear as a line of points at $x=23$:
Resta to Ericcson.  Note also Palmer and Alonso who managed to score a
F1 point but rank below Ericcson according to Bradley-Terry.

But overall there
seems to be some degree of correlation between the two, and
differences in detail.
